---
title: "Step-by-step illustration of MIMS-unit algorithm"
output: rmarkdown::html_vignette
author: "Qu Tang"
date: "Oct 12, 2019"
vignette: >
  %\VignetteIndexEntry{pkgdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(plyr)
require(dplyr)
require(ggplot2)
```



Here we demonstrate the scripts used to reproduce the diagram.

### Original data

We use a one-second segment of raw accelerometer signal (80 Hz, 8g) from a random subject doing jumping jack as test data. The other signals with different sampling rates and dynamic ranges are simulated via the `simulated_new_data` function. The step-by-step illustration has been presented as Figure 1 in the manuscript.


```{r, echo=TRUE}
df = MIMSunit::conceptual_diagram_data
start_time = df[[1,1]]
stop_time = start_time + 1
```

#### Illustration of the original signals

```{r echo=TRUE, fig.height=2, fig.width=10, message=FALSE, warning=FALSE, out.width="100%"}
figs = df %>% 
  group_by(.data$NAME) %>%
  MIMSunit::clip_data(start_time = start_time, stop_time = stop_time) %>%
  group_map(
    ~ MIMSunit::illustrate_signal(
      .x,
      title = .y,
      line_size = 1,
      point_size = 1,
      range = c(-.x$GRANGE[1], .x$GRANGE[1])
    ) + theme(plot.margin = unit(c(0, 0.01, -0.2, -0.2), "line"))
  )
gridExtra::grid.arrange(grobs = figs, nrow = 1)
```

1. Dashed lines represent the dynamic range region. Beyond this line, signals will be maxed out as shown in Device 1-3.

### Interpolation: Upsampling to 100Hz

The second step is to regularize the sampling rates of the signals and upsample the signal to __100 Hz__, because we have shown extrapolation (see next section) works better and more robustly at __100 Hz__ than lower sampling rates. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
oversampling = function(df, name) {
  out_df = data.frame(MIMSunit::.extrapolate_oversampling(df$HEADER_TIME_STAMP, df$X))
  out_df$SR = df$SR[1]
  out_df$GRANGE = df$GRANGE[1]
  out_df$NAME = name[[1]]
  out_df = as.data.frame(out_df)
  return(out_df)
}
interp_df = df %>% group_by(.data$NAME) %>%
  group_map(
    ~ oversampling(.x, name = .y)
  ) %>% rbind_list
colnames(interp_df) = c('HEADER_TIME_STAMP', 'X', 'SR', 'GRANGE', 'NAME')
```

#### Illustration of the interpolated signals

```{r echo=TRUE, fig.height=2, fig.width=10, message=FALSE, warning=FALSE, out.width="100%"}
figs = interp_df %>%
  group_by(.data$NAME) %>%
  MIMSunit::clip_data(start_time = start_time,
                         stop_time = stop_time) %>%
  group_map(
    ~ MIMSunit::illustrate_signal(
      .x,
      title = .y[[1]],
      line_size = 1,
      point_size = 1,
      range = c(-.x$GRANGE[1], .x$GRANGE[1])
    ) + theme(plot.margin = unit(c(0, 0.01, -0.2, -0.2), "line"))
  )
gridExtra::grid.arrange(grobs = figs, nrow = 1)
```

### Extrapolation: Restoring "maxed-out" samples

The third step is to restore the samples that are maxed out due to low dynamic range for signals of intensive movement. Please check the manuscript for the details of the extrapolation algorithm.

<summary>
<details>
```{r echo=TRUE, message=FALSE, warning=FALSE}
extrapolation = function(df, name, start_time, stop_time) {
  markers = MIMSunit::.extrapolate_mark("gamma")(df$HEADER_TIME_STAMP, 
                                                 df$X, -df$GRANGE[1], 
                                                 df$GRANGE[1], 
                                                 0.03)
  markers_df = data.frame(HEADER_TIME_STAMP = df$HEADER_TIME_STAMP,
                          X = abs(markers))
  neighbors = MIMSunit::.extrapolate_neighbor(markers, 100, 0.05)
  if (nrow(neighbors) > 0) {
    left_indices = c()
    right_indices = c()
    mo_indices = c()
    for (i in 1:nrow(neighbors)) {
      left_indices = c(left_indices,
                       neighbors$left_start[i]:neighbors$left_end[i])
      right_indices = c(right_indices,
                        neighbors$right_start[i]:neighbors$right_end[i])
      mo_indices = c(mo_indices,
                     neighbors$left_end[i]:neighbors$right_start[i])
    }
    fitted_line_df = MIMSunit::.extrapolate_fitline(
      df[[1]],
      df[[2]],
      neighbors,
      markers,
      0.6,
      100,
      0.05
    )
    colnames(fitted_line_df) = c('HEADER_TIME_STAMP', 'X', 'type', 'index')
    left_neighbors_df = df[left_indices, ] %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time) %>% data.frame
    right_neighbors_df = df[right_indices, ] %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time) %>% data.frame
    between_neighbor_df = df[c(-left_indices, -right_indices), ] %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time)%>% data.frame
    between_neighbor_without_maxed_out_df = df[c(-left_indices, -right_indices, -mo_indices), ] %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time) %>% data.frame
    maxed_out_df = df[mo_indices, ] %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time) %>% data.frame
    maxed_out_df$weight = markers_df[mo_indices, 'value'] %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time)
    fitted_line_df = fitted_line_df %>%
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time) %>% data.frame
    points_ex_df = fitted_line_df[fitted_line_df$type == 'point', c(1, 2)]
  } else {
    marks_df = NULL
    left_neighbors_df = NULL
    right_neighbors_df = NULL
    maxed_out_df = NULL
    between_neighbor_df = NULL
    between_neighbor_without_maxed_out_df = NULL
    fitted_line_df = NULL
    points_ex_df = NULL
  }
  df = df %>% 
      MIMSunit::clip_data(start_time = start_time, 
                             stop_time = stop_time) %>% data.frame
  return(
    list(
      data.frame(df),
      between_neighbor_df,
      left_neighbors_df,
      right_neighbors_df,
      maxed_out_df,
      between_neighbor_without_maxed_out_df,
      markers_df,
      fitted_line_df,
      points_ex_df,
      name[[1]]
    )
  )
}
```
</details>
</summary>

```{r echo=TRUE}
extrap_illustration_list = interp_df %>% group_by(.data$NAME) %>%
  group_map( ~ extrapolation(
    .x,
    name = .y,
    start_time = start_time,
    stop_time = stop_time
  ))
```

#### Illustration of extrapolation algorithm

```{r echo=TRUE, fig.height=2, fig.width=10, message=FALSE, warning=FALSE, out.width="100%"}
draw_extrapolation = function(extrap_illustration) {
  df = extrap_illustration[[1]]
  between_neighbors_df = extrap_illustration[[2]]
  left_neighbors_df = extrap_illustration[[3]]
  right_neighbors_df = extrap_illustration[[4]]
  extrap_points_df = extrap_illustration[[9]]
  fitted_line_df = extrap_illustration[[8]]
  p = MIMSunit::illustrate_extrapolation(
    df = df,
    between_neighbor_df = between_neighbors_df,
    title = extrap_illustration[[10]],
    left_neighbors_df = left_neighbors_df,
    right_neighbors_df = right_neighbors_df,
    show_neighbors = TRUE,
    extrap_points_df = extrap_points_df,
    fitted_line_df = fitted_line_df,
    show_extrapolated_points_and_lines = TRUE
  ) + theme(plot.margin = unit(c(0, 0.01, -0.2, -0.2), "line"))
  return(p)
}
figs = lapply(extrap_illustration_list, draw_extrapolation)
gridExtra::grid.arrange(grobs = figs, nrow = 1)
```

