---
title: "Cross device consistency of MIMS-Unit algorithm"
output: rmarkdown::html_vignette
author: "Qu Tang"
date: "May 22, 2018"
vignette: >
  %\VignetteIndexEntry{Cross device consistency of MIMS-Unit algorithm}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(plyr)
require(dplyr)
require(ggplot2)
```

### Introduction

This is a replication of Figure 3 in the manuscript. The consistency test is run with the following devices on an orbital shaker with RPM ranging from 60 (approx. 1 Hz) to 480 (approx. 8Hz).

```{r, include=FALSE}
df = MIMSunit::measurements_different_devices
device_table = df %>% ddply(
  c('NAME'),
  summarise,
  SR = head(.data$SR, 1),
  GRANGE = head(.data$GRANGE, 1),
  DEVICE = head(.data$DEVICE , 1)
)
device_table = device_table[c('DEVICE', 'SR', 'GRANGE')]
colnames(device_table) = c('DEVICE', 'SAMPLING RATE (Hz)', 'DYNAMIC RANGE (g)')
```
```{r, echo = FALSE}
knitr::kable(device_table)
```

The collected dataset is then processed by three accelerometer data summary algorithms for comparison.

1. Actigraph counts (processed using Actilife software)
2. [ENMO](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0164045) (used by UK Biobank project)
3. [MIMS-Unit](https://mhealthgroup.github.io/MIMSunit/) (used by NHANES project)

_The collected data is calibrated using at least 24h wearing data when applying ENMO algorithm as suggested in the paper. The other two algorithms do not require specific calibration unless the calibration is suggested by device manufacturers._

### Coefficient of variety of three accelerometer data summarizations cross different devices

```{r, echo=FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.width=10,fig.height=8}
p1 = ggplot(
  MIMSunit::cv_different_algorithms,
  aes(
    x = .data$HZ,
    y = .data$COEFF_OF_VARIATION,
    linetype = .data$TYPE,
    shape = .data$TYPE,
    colour = .data$TYPE
  )
) +
  
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  ylim(0, 1) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.margin = unit(10 ^ -3, 'inch'),
    panel.margin = unit(0.1, 'inch'),
    axis.text = element_text(margin = margin(0, 0, 0, 0), size = 16),
    text = element_text(size = 16),
    plot.margin = margin(0, 0, 0, 0, 'inch'),
    strip.background = element_blank(),
    legend.key = element_blank()
  ) +
  scale_colour_discrete(name = "Device") +
  scale_shape_discrete(name = "Device") +
  guides(
    shape = guide_legend(ncol = 2, title = NULL),
    linetype = guide_legend(ncol = 2, title = NULL),
    colour = guide_legend(ncol = 2, title = NULL)
  ) +
  ylab("Coefficient of variance (CV)") +
  xlab("Frequency (Hz)")

p1
```



### Accelerometer data summarizations for different devices

```{r, echo=FALSE, message=FALSE, warning=FALSE, out.width = "100%", fig.width=10,fig.height=24}
p2 = ggplot(
  data = MIMSunit::measurements_different_devices,
  aes(
    x = .data$HZ,
    y = .data$mean,
    color = .data$NAME,
    linetype = .data$NAME
  )
) +
  geom_line(size = 1.2) + geom_point(aes(shape = .data$NAME), size = 3) +
  scale_colour_discrete(name = "Device") +
  scale_shape_discrete(name = "Device") +
  facet_wrap( ~ TYPE, ncol = 1, scales = "free_y") +
  guides(
    shape = guide_legend(ncol = 3, title = NULL),
    linetype = guide_legend(ncol = 3, title = NULL),
    colour = guide_legend(ncol = 3, title = NULL)
  ) +
  ylab("Activity Counts") + xlab("Frequency (Hz)") +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.margin = unit(10 ^ -3, 'inch'),
    panel.margin = unit(0.1, 'inch'),
    axis.text = element_text(margin = margin(0, 0, 0, 0), size = 16),
    text = element_text(size = 16),
    plot.margin = margin(0, 0, 0, 0, 'inch'),
    strip.background = element_blank(),
    legend.key = element_blank()
  )
p2
```