---
title: "Deciding truncation threshold"
output: rmarkdown::html_vignette
author: "Qu Tang"
date: "Jul 04, 2018"
vignette: >
  %\VignetteIndexEntry{pkgdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(magrittr)
require(dygraphs)
```

Unlike Actigraph count algorithm, MIMS unit algorithm truncates non-zero values caused by floating number precision limit and the imperfect filtering transition band during MIMS unit computation. This article describes the process of deciding the truncation threshold.

### MIMS unit value of constant signal

The constant signal has zero variance.


```{r load_data_long, warning=FALSE, message=FALSE, include=FALSE}
st = Sys.time()
ts = seq(st, st + 300, length = 300 * 80)
x = rep(1, length(ts))
y = rep(0, length(ts))
z = rep(0, length(ts))
df = data.frame(HEADER_TIME_STAMP = ts, X=x, Y=y, Z=z)
```

#### Input data
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2.5, out.width='100%'}
require(dygraphs)
df_xts = xts::xts(df[,2:4], df[,1])
dygraphs::dygraph(df_xts) %>% dygraphs::dyRangeSelector() %>% dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) %>% dyLegend(width = 400) %>% dyAxis("y", label = "Acceleration (g)", valueRange = c(-2, 2))
```

```{r echo=TRUE, message=FALSE, warning=FALSE, results = 'hide'}
mims = MIMSunit::custom_mims_unit(df, epoch = '1 sec', dynamic_range = c(-6, 6), allow_truncation = FALSE, output_mims_per_axis = TRUE)
```

#### Output: MIMS unit values
```{r echo=FALSE, fig.height=2.5, message=TRUE, warning=FALSE, out.width='100%'}
mims_xts = xts::xts(mims[,2:5], mims[,1])
dygraphs::dygraph(mims_xts) %>% dygraphs::dyRangeSelector() %>% dyOptions(colors = RColorBrewer::brewer.pal(1, "Set2"), drawPoints=TRUE, pointSize=2) %>% dyLegend(width = 400) %>% dyAxis("y", label = "MIMS unit")
```

The output MIMS unit values have high shoot up at the beginning due to the nonlinear phase response of butterworth filter. It takes about 1 min for the output signal to stablize. Although the signal is constant, the MIMS unit values are not zeros, which is caused by floating number precision limit during MIMS unit computation (filtering).

The median value after stablization is 
```{r echo=FALSE, message=FALSE, warning=FALSE}
lower_bound = median(mims[61:nrow(mims),2])
print(lower_bound)
```
And the standard deviation is
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(sd(mims[61:nrow(mims),2]))
```

### MIMS unit value of accelerometer signal when a device is resting on a table

The original signal has variance,
```{r, include=FALSE, warning=FALSE}
wd = getwd()
if(stringr::str_detect(wd, "articles")){
  file_path = normalizePath(file.path(wd, "../../vignettes/data/rest_on_table.csv"))
}else{
  file_path = normalizePath(file.path(wd, "../vignettes/data/rest_on_table.csv"))
}
options(digits.secs=3)
```

```{r, warning=FALSE, message=FALSE, include=FALSE}
df = MIMSunit::import_mhealth_csv(filepath=file_path)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
print(sprintf('X axis variance: %e', sd(df[,2])))
print(sprintf('Y axis variance: %e', sd(df[,3])))
print(sprintf('Z axis variance: %e', sd(df[,4])))
```

#### Input data
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2.5, out.width='100%'}
require(dygraphs)
df_xts = xts::xts(df[,2:4], df[,1])
dygraphs::dygraph(df_xts) %>% dygraphs::dyRangeSelector() %>% dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) %>% dyLegend(width = 400) %>% dyAxis("y", label = "Acceleration (g)", valueRange = c(-2, 2))
```

```{r echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
mims = MIMSunit::custom_mims_unit(df, epoch = '1 sec', dynamic_range = c(-6, 6), allow_truncation=FALSE, output_mims_per_axis = TRUE)
```

#### Output: MIMS unit values
```{r, echo=FALSE, fig.height=2.5, out.width='100%', message=FALSE, warning=FALSE}
mims_xts = xts::xts(mims[,2:5], mims[,1])
dygraphs::dygraph(mims_xts) %>% dygraphs::dyRangeSelector() %>% dyOptions(colors = RColorBrewer::brewer.pal(1, "Set2"), drawPoints=TRUE, pointSize=2) %>% dyLegend(width = 400) %>% dyAxis("y", label = "MIMS unit")
```

The output MIMS unit values have high shoot up at the beginning due to the nonlinear phase response of butterworth filter. It takes about 1 min for the output signal to stablize. The MIMS unit algorithm outputs non-zero values, which is caused by flutuation of electronic current of hardware.

The median value after stablization is
```{r echo=FALSE, message=FALSE, warning=FALSE}
upper_bound = median(mims[61:nrow(mims),2])
print(sprintf('%e', upper_bound))
```
And the standard deviation is
```{r echo=FALSE, message=FALSE, warning=FALSE}
print(sprintf('%e', sd(mims[61:nrow(mims),2])))
```

### Conclusion
According to the analysis, a proper truncation threshold for MIMS unit value (1 second bout) can be one numerical magnitude above the larger value of the two cases above, which may be set at `1e-4`.

Therefore, the truncation threshold for a given MIMS unit at `t` epoch length will be,

$$0.0001 \times t$$